---
title: "Frequently asked questions for speakers, session chairs, and panelists"
date: "Last change: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  rmarkdown::html_document:
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

```{r setup, include = FALSE, echo = FALSE}
## load packages
packs.html <- c("knitr", "pander", "reporttools", "dplyr", "readxl")
for (i in 1:length(packs.html)){library(packs.html[i], character.only = TRUE)}

knitr::opts_chunk$set(echo = TRUE)

## read in data
path <- getwd()
past <- as.data.frame(read_excel(paste(path, "/data/past.xlsx", sep = ""), col_types = NULL))
sci22 <- as.data.frame(read_excel(paste(path, "/data/2022/scicom2022.xlsx", sep = ""), col_types = NULL))
waived <- as.data.frame(read_excel(paste(path, "/data/waived.xlsx", sep = ""), col_types = NULL))
reg <- as.data.frame(read_excel(paste(path, "/data/registration.xlsx", sep = ""), col_types = NULL))

# last issue 
last <- 2022

source(paste(path, "/functions/colFmt.r", sep = ""))
```

# Introduction

You have agreed to contribute to the `r paste("[EFSPI regulatory statistics workshop ", last + 1, "](", past[past[, "Year"] == last + 1, "Program"], ")", sep = "")`. Many thanks for that!

# Scope and contact

This document provides necessary information for contributors to the workshop. For any further questions please do not hesitate to reach out to one of the [local organizing committee members](local.html).

# Program

`r paste("[EFSPI regulatory statistics workshop ", last + 1, "](", past[past[, "Year"] == last + 1, "Program"], ")", sep = "")`.

# Registration

Please register yourself using `r paste("[this form](", reg[reg[, "Year"] == last + 1, "Registration"], ")", sep = "")`. 

# Benefits

As a premise note that [EFSPI](https://efspi.org/) is non-profit making and as a principle does not pay an honorarium. 

However, for students, members of the Scientific Program Committee, session chairs, presenters, poster presenters, and invited panelists we are able to offer the following benefits, depending on your affiliation:

```{r, include=TRUE, echo=FALSE}
waived[is.na(waived)] <- ""
kable(waived, align = "llccccc")
```
However, please still register using `r paste("[this form](", reg[reg[, "Year"] == last + 1, "Registration"], ")", sep = "")`. 

For reimbursement please complete [this form](data/2022/20220914_EFSPI_workshop_reimbursement.doc) and send it to [Egbert Biesheuvel](mailto:egbert.biesheuvel@viatris.com).

# Hotels

We ask you to book your travel and accommodation yourself. We have reserved rooms at the following hotels:

- [Hotel Spalentor](http://www.hotelspalentor.ch).
  - 8 min walk from venue.
  - 8 rooms blocked for 1 night (14 – 15 Sept) until 2nd August 2022.
  - Rate = 163 CHF excl breakfast, plus city tax (4CHF).
  - There are no single rooms available, so it would be double rooms for 1 person.
  - Book directly via email to info@hotelspalentor.ch with keyword "EFSPI 2022".
- [Hotel Odelya](http://www.odelya.ch) (this is the Bildungszentrum where we used to stay before the pandemic).
  - 9 min walk from venue.
  - 15 rooms blocked for 1 night (14 – 15 Sept) until 3rd August.
  - Rate = 209 CHF incl breakfast, plus city tax (4 CHF).
  - There are no single rooms available, so it would be double rooms for 1 person.
  - Book directly via email hotel@odelya.ch with keyword "EFSPI 2022".
- [Hotel D](https://www.hoteld-basel.ch/en/).
  - 11 min walk from venue.
  - 15 rooms blocked for 1 night (14 – 15 Sept) until 13th August 2022.
  - Rate = 180 CHF incl breakfast & city tax.
  - Book directly via email basel@hoteld.ch with keyword "EFSPI 2022".

We invite everyone to book these rooms themselves. The offers end at the given date or when all blocked rooms have been booked.

# Posting of presentations on EFSPI webpage

After the workshop, we would like to post presentation slide decks and recordings of the webinars to the EFSPI webpage (see `r paste("[here](", past[past["Year"] == last, "Slidedecks"], ")", sep = "")` for the `r last` issue). Please let us know in case you would prefer NOT to post your slides and/or the recording to the EFSPI webpage.

# Recording

If possible we would like to record the session and post it on the EFSPI webpage (see `r paste("[EFSPI regulatory statistics workshop ", last, "](", past[past[, "Year"] == last, "Slidedecks"], ")", sep = "")` for the `r last` issue). Please do let us know in case you would prefer NOT to be recorded. If $\ge 1$ contributor opts out of recording we will not record the entire session.

# Slidedecks and short bio

We would be very grateful to receive a stable draft of your presentation slidedeck by `r colFmt("5th September 2022", "red")`. This, in order to be flexible and to potentially run the slides from our end in case of issues with the internet connection.

We would also appreciate if you could share with us a short paragraph that the session chairs will use to introduce you during the session.

Please send all these materials to [Kaspar Rufibach](mailto:kaspar.rufibach@roche.com) and cc: your respective session chairs.

# Technical setup and how we plan to run the sessions

- The conference will run as hybrid, i.e. with participants in the room and online.
- The webinar tool that we will most likely use is Zoom. The dial-in details will be added to the invite (which is already in your calendar) in due time.
- We will open the Zoom session at least 30min prior to the scheduled starting date and invite everyone to dial in early.
- Preference is to run the slides centrally by the chairs. However, speakers can opt to drive the slides themselves. If you prefer to do so please familiarize yourself with Zoom and your own setup such that transitions from one speaker to the next can be made efficiently.
- We will invite attendees to ask questions in the Zoom chat. Every attendee can see them. The chairs will structure them and ask them in the panel discussion.
- Chairs will decide whether to ask questions directly after the presentations or to hold them until the panel discussion.

# Poster presentations

Panels for poster presenters will be available. Poster should be the usual standard format (we can cater up to A0). The idea is that at least during the official lunch & poster session (14th September 12:30-15:00) that you would be near your poster and discuss and answer questions of participants.

# Questions?

For feedback and questions send an email to [info@efspiworkshop.org](mailto:info@efspiworkshop.org).



